### 2021-11-12 NSF2021/Description/specificaim1.tex
made it to part way through SA1

  \begin{figure}[h!]
\begin{center}
  \includegraphics[width=0.8\textwidth]{figures/SpecificAim1/Domain.pdf}
\end{center}  
  \caption{\label{fig:flow_map} A collection of 3D
   amphiphilic particles suspended in a solvent. The solvent velocity
   satisfies the Stokes equations, and the hydrophobic forces depend on
   the solvent activity that satisfies the screened Laplace equation.
   The geometry is updated by solving the mobility problem.}     
  \end{figure}

The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{alignat}{3}
\label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
\label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant
solvent viscosity. The domain
$\Omega$ is the fluid region surrounding the particles.
Since the particles are rigid, the solvent velocity 
satisfies a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$
with translational velocity $\vv_i$ and
angular velocity $\omega_i$.
Given imposed forces acting on each particle,
the \emph{mobility problem} consists of finding
translational and angular velocities so that 
viscous fluid forces balance the imposed forces.

The hydrophobic interactions come from the tendency 
of particles to minimize the free energy of the structure of
the surrounding water molecules.  
Experimental measurements suggest that the free energy functional
take the form 
\begin{equation}
\label{eq:free_energy}
F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
\end{equation}
where
$u$ is an order parameter for the structure of water,
$\rho$ is a decay length,
$C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
Since waters reorient 
on a time scale much smaller than for the particle motion, 
then at each moment in time $u$ minimizes $F[u]$ and satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
\text{ on } \Omega.
\end{equation}
The boundary condition $g$ that imposes 
the water structure at the water-hydrocarbon interfaces.
It is a material label that is transported with the particle motions.

The coupling between the Stokes equations \eqref{eq:stokes1}-\eqref{eq:stokes3}
and the semilinear elliptic equation \eqref{eq:SL}
comes from the first variation of the energy functional.
The particles minimize the free energy $F[u]$
by altering the location of hydrophobic interfaces. 
It is possible to calculate the rate of change of $F[u]$
using variation of the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho  \left(|\nabla u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$ along the
particle boundary.
The density \eqref{eq:stress}  was first introduced
by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue of
disjoining pressure calculated by
\cite{MaRa76, ErLjCl89, KoNa15, Nagle17, KUZMIN2005}.
It is the mathematical ingredient responsible for forming particle
aggregates that sequester their hydrophobic surface regions.

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
    \end{center}
  \caption{
    Self assembly with a polar boundary condition leads to checkboard pattern.
    Green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    \label{fig:self-assemblyA}}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}  
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}\\
\end{center}    
\caption{With an amphiphilic boundary condition particles self-assemble
  into bilayers. The patterning shields the hydrophobic core (yellow) from the
  aqueous phase. 
      \label{fig:self-assemblyA}}
\end{figure}
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and are accounted for as follows.
The hydrophilic side takes the value $u = 0$ since the
apolar headgroup of a lipid, for example, does not alter the structure
of adjacent waters. The hydrophobic side takes the value $u > 0$. 
The interaction between particles is attractive. Using
$(3\pi )^{-1/2}(1 + \cos(\theta_i(\mathbf{x})))$
as a simple modification to the previous boundary condition 
produces two-dimensional micelles and bilayers \cite{Fu2018_SIAM}.
Researchers have asked us if the phenomenon is robust. To show
that it is, we use 
\begin{equation}
\label{eq:vonMises}
g_i(\mathbf{x}) =
\sqrt{
  \frac{\exp( \kappa_i(\theta_i(\mathbf{x}) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}
\end{equation}
instead where the radicand is the von Mises 
distribution with director angle $\theta^0_i$ and Bessel function
$I_0$ of order zero. The square of this function behaves as a normal
distribution with variance like $1/\kappa_i$. To replicate
experimental conditions, the concentration $\kappa_i$ and radii
$r_i$ are randomized. Using the same initial configuration, the
particles form small groups. The small groups combine to form bilayers.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
    \caption{This figure is for hydrophobic particles with a bias. The
      hydrophobic intensity is greater on one side of the particle (magenta)
      than the other (yellow).
    \label{fig:self-assemblyA}}
\end{center}
\end{figure}

@@

This yields a dissipation of the total potential \eqref{eq:total_poten},
which stabilizes the evolving bilayer shape.  Therefore, we reconstruct
an evolving monolayer dividing surface $\Sigma$ and director field ${\bf
n}$ by interpolating the particle centers and orientations. Using
\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the
interpolated shapes.

>>>>

%\begin{wrapfigure}[h!]
\begin{wrapfigure}[9]{r}{0.55\textwidth}
  \centering
  \vspace{-20pt}
  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
  \caption{\label{fig:flow_map} A collection of amphiphilic particles
  suspended in a solvent. The solvent velocity satisfies the Stokes
  equations, and the hydrophobic forces depend on the solvent activity
  that satisfies the screened Laplace equation. The geometry is updated
  by solving the mobility problem.}
\end{wrapfigure}

The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant
solvent viscosity. The domain
$\Omega$ is the fluid region surrounding the particles.
Since the particles are rigid, the solvent velocity 
satisfies a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$
with translational velocity $\vv_i$ and
angular velocity $\omega_i$.
Given imposed forces acting on each particle,
the \emph{mobility problem} consists of finding
translational and angular velocities so that 
viscous fluid forces balance the imposed forces.

The hydrophobic interactions come from the tendency 
of particles to minimize the free energy of the structure of
the surrounding water molecules.  
Experimental measurements suggest that the free energy functional
take the form 
\begin{equation}
\label{eq:free_energy}
F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
\end{equation}
where
$u$ is an order parameter for the structure of water,
$\rho$ is a decay length,
$C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
Since waters reorient 
on a time scale much smaller than for the particle motion, 
then at each moment in time $u$ minimizes $F[u]$ and satisfies 
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle motions (Figure~\ref{fig:bcs}).

\begin{wrapfigure}[10]{r}{0.65\textwidth}
  \vspace{-22pt}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
\caption{\label{fig:bcs} Boundary conditions characterize the type of
  water structure: an amphiphilic particle (left), a hydrophobic
  particle with anisotropic intensity (middle), a water structure with
  plus/minus polarity (right). The dashed curve is the boundary of the
  disk and the arrow its director.}
\end{wrapfigure}
The coupling between the Stokes equations \eqref{eq:stokes} and the
semilinear elliptic equation \eqref{eq:SL} comes from the first
variation of the energy functional.  The particles minimize the free
energy $F[u]$ by altering the location of hydrophobic interfaces.  It is
possible to calculate the rate of change of $F[u]$ using variation of
the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.  Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho  \left(|\nabla u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right].
\end{align}
The imposed forces and torques from the integration of $\mathbf{T}$ along the
particle boundary.
The density \eqref{eq:stress}  was first introduced
by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue of
disjoining pressure calculated by
\cite{MaRa76, ErLjCl89, KoNa15, Nagle17, KUZMIN2005}.
It is the mathematical ingredient responsible for forming particle
aggregates that sequester their hydrophobic surface regions.

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
    \end{center}
  \caption{ Self assembly with a polar boundary condition leads to
  checkboard pattern.  Green is for $u < 0$, yellow is for $u > 0$, and
  blue is for $u = 0$.
    \label{fig:self-assemblyA}}
\end{figure}
\todo{This figure is not referenced in the text.}

@@

\begin{figure}[h!]
\begin{center}  
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}\\
\end{center}    
\caption{With an amphiphilic boundary condition particles self-assemble
  into bilayers. The patterning shields the hydrophobic core (yellow) from the
  aqueous phase. 
      \label{fig:self-assemblyB}}
\end{figure}
\todo{This figure is not referenced in the text.}
Amphiphilic particles have a hydrophobic tail and a hydrophilic head
and are accounted for as follows.
The hydrophilic side takes the value $u = 0$ since the
apolar headgroup of a lipid, for example, does not alter the structure
of adjacent waters. The hydrophobic side takes the value $u > 0$. 
The interaction between particles is attractive. Using
$(3\pi )^{-1/2}(1 + \cos(\theta_i(\mathbf{x})))$
as a simple modification to the previous boundary condition 
produces two-dimensional micelles and bilayers \cite{Fu2018_SIAM}.
Researchers have asked us if the phenomenon is robust. To show
that it is, we use 
\begin{equation}
\label{eq:vonMises}
g_i(\mathbf{x}) =
\sqrt{
  \frac{\exp( \kappa_i(\theta_i(\mathbf{x}) - \theta^0_i))}
  {2\pi r_i I_0(\kappa_i)}}
\end{equation}
instead where the radicand is the von Mises 
distribution with director angle $\theta^0_i$ and Bessel function
$I_0$ of order zero. The square of this function behaves as a normal
distribution with variance like $1/\kappa_i$. To replicate
experimental conditions, the concentration $\kappa_i$ and radii
$r_i$ are randomized. Using the same initial configuration, the
particles form small groups. The small groups combine to form bilayers.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
    \caption{This figure is for hydrophobic particles with a bias. The
      hydrophobic intensity is greater on one side of the particle (magenta)
      than the other (yellow).
    \label{fig:self-assemblyC}}
\end{center}
\end{figure}
\todo{This figure is not referenced in the text.}

@@

This yields a dissipation of the total potential \eqref{eq:total_poten},
which stabilizes the evolving bilayer shape. Therefore, we reconstruct
an evolving monolayer dividing surface $\Sigma$ and director field ${\bf
n}$ by interpolating the particle centers and orientations.
Using~\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$
from the interpolated shapes.
